---
title: "classification"
author: "cshb26"
date: "3/19/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("tidyverse")
library("ggplot2")
```


## Problem Description

### Description of the data and the explanation of the objective of the analysis

```{r}
hotels = readr::read_csv("https://www.louisaslett.com/Courses/MISCADA/hotels.csv")
View(hotels)
```

### Initial data summary

```{r}
skimr::skim(hotels)
```

### 整理数据
画图发现adr>5000，故Drop the extreme point (adr > 5000)
同时设置total_nights变量取代两个stays
同时设置kids变量取代children和babies
Drop `reservation_status` and `reservation_status_date`
```{r}
hotels <- hotels %>%
  filter(adr < 4000) %>% 
  mutate(total_nights = stays_in_weekend_nights+stays_in_week_nights) %>% 
  mutate(kids = case_when(
    children + babies > 0 ~ "kids",
    TRUE ~ "none"
  ))

hotels <- hotels %>%
  select(-stays_in_weekend_nights, -stays_in_week_nights) %>%
  select(-babies, -children) %>%
  select(-reservation_status, -reservation_status_date) 
```

```{r}
skimr::skim(hotels)
```

### Simple visualisations of the data

```{r}
ggplot(hotels,
       aes(x = adr, y = stays_in_weekend_nights+stays_in_week_nights)) +
  geom_point(alpha=0.1)
```


## Model fitting

下面这些相关度不高或值较多，舍弃meal、country、market_segment、distribution_channel、agent、company、days_in_waiting_list、required_car_parking_spaces、reserved_room_type和assigned_room_type
```{r}
hotels <- hotels %>%
  select(-meal, -country, -market_segment, -distribution_channel, -agent, -company, -days_in_waiting_list, -required_car_parking_spaces, -reserved_room_type, -assigned_room_type)
```



### any train/test/validate, cross-validation, nested resampling or bootstrap strategies employed




### the approach taken to fitting, including any design, loss function, early stopping criteria, and algorithm choices




## Model improvements

### what model was finally selected and why


### summaries of different approaches tried before selecting the final model



### hyperparameter selection or tuning to improve model fits


### insights into improvements achieved through different architectures (deep learning), data augmentation approaches, regularisation methods, etc



## Performance report

### details on the performance of the model, including calibration



### reporting and justification of objective function choices



### would you be more worried about false negatives or false positives in this problem, and how could you address that concern

